Enhance Road Detection Data Processing of LiDAR Point Clouds to Specifically Identify Unmarked Gravel Rural Roads

### 2023-05-03 Huston_Paper_asme.tex
what is bayesian

	{Classification of five rosbags with data gathered from a section of road with three intercepting gravel driveways (one of the gravel driveways was the entrance to the source of the gravel training data). Three arcs from three channels were considered for classification - the centers of the arcs were directly in front of the vehicle, and 45 degrees left and right of center, creating nine total areas in a 3x3 grid in front of the van. Following the same process as aggregating point clouds, GNSS and IMU data informed the location and orientation of the arcs in each 360 degree scan.}

	{Manually defined gravel, asphalt, and side-of-road areas were projected onto the averaged coordinates of all the classified arcs. Manually defined gravel, asphalt, and side-of-road areas were then examined for the number of type of classified arcs, yielding the accuracy scores for each area. Classified point clouds were then manually examined to determine if the location of gravel and asphalt surfaces may be identified. If consecutive points from each channel in any direction had two or more matching gravel or asphalt classification and was evenly spaced, a gravel or road surface area was projected. Guessed road surface areas were then compared to actual areas to determine the method's ability at unmarked gravel road discovery.}

>>>>

	{Classification of five rosbags with data gathered from a section of road with three intercepting gravel driveways (one of the gravel driveways was the entrance to the source of the gravel training data). Three arcs from three channels were considered for classification - the centers of the arcs were directly in front of the vehicle, and 45 degrees left and right of center, creating nine total areas in a 3x3 grid in front of the van. Following the same process as aggregating point clouds, GNSS and IMU data informed the location and orientation of the arcs in each 360 degree scan. All arcs were then classified as "asphalt", "gravel", or "unknown", and the averaged coordinates of each arc was aggregated into a single, classified point cloud.}

	{Manually defined gravel, asphalt, and side-of-road areas were projected onto the classified point cloud. Manually defined gravel, asphalt, and side-of-road areas were then used to determine the accuracy of the terrain classification algorithm. Classified point clouds were then manually examined to determine if the location of gravel and asphalt surfaces may be identified. If consecutive points from each channel in any direction had two or more matching gravel or asphalt classification and was evenly spaced, a gravel or road surface area was projected. Guessed road surface areas were then compared to actual areas to determine the method's ability at unmarked gravel road discovery.}
